Supplementary Appendix

### 2023-11-22 manuscript/supplement.qmd
smaller adjustment to modified supplement version

@@

### Reproducible R computing environments

@@

```{r}
renv::restore()
```

@@

```{r}
sessionInfo()
```

### Absolute versus relative paths

@@

```{r}
icd_codes <- read.csv('C:/User/Projects/rwe_study/protocol/icd_codes.csv')
```

@@

```{r}
library(here)
icd_codes <- read.csv(here("protocol", "icd_codes.csv"))
```

#

@@

>>>>

Besides the usage of `Git` and remote repositories as a version control systems, there are further relevant aspects that determine the reproducibility of analytic code when using open-source software such a R. To complement the introduction and discussion on `Git` in the main manuscript, we here want to elaborate on a few further considerations of computational reproducibility when using R.

@@

## Reproducible R computing environments

@@

```{r}
#| eval: false
#| echo: true

renv::restore()
```

@@

```{r}
#| eval: false
#| echo: true

sessionInfo()
```

## Absolute versus relative paths

@@

```{r}
#| eval: false
#| echo: true

icd_codes <- read.csv('C:/User/Projects/rwe_study/protocol/icd_codes.csv')
```

@@

```{r}
#| eval: false
#| echo: true

library(here)
icd_codes <- read.csv(here("protocol", "icd_codes.csv"))
```

@@

# References {.unnumbered}

::: refs
:::
